Physcraper: Body

### 2020-07-02 2-body.Rmd
jessica comments

More than a decade ago, the National Center for Biodiversity Information (NCBI) molecular database, GenBank, released its version number 159 (April 15, 2007). With 72 million DNA sequences, it was estimated to have the potential to resolve evolutionary relationships of most of the 241 000 distinct taxa represented in it [about `r round(236023/240708, digits=4)*100`% of taxa in the NCBI taxonomy; @sanderson2008phylota], which in turn covers about 10% of extant described biodiversity [taking a conservative estimate of extant diversity; @scott2011ncbi; @federhen2003taxonomy].
In comparison, the current GenBank release number 238 (June 15, 2020) has tripled in size, hosting data for more than 217 million DNA sequences [(See GenBank's release website)](https://ftp.ncbi.nih.gov/genbank/gbrel.txt). Yet, we only have data on phylogenetic relationships available for about 90 000 taxa [@hinchliff2015synthesis; CURRENT SYNTH TREE CITATION], covering less than one third of the taxonomic diversity with data available a decade ago. Some of this discrepancy is explained by the many phylogenies that are not publicly shared [@drew2013lost; @magee2014dawn, @mctavish2018bioessay]. However, most recently published large trees have been made available in recent years, indicating there is also a lag between the amount of new DNA data generated and the analysis of these data in a phylogenetic context.

>>>>

More than a decade ago, the National Center for Biodiversity Information (NCBI) molecular database, GenBank, released its version number 159 (April 15, 2007). With 72 million DNA sequences, it was estimated to have the potential to resolve evolutionary relationships of most of the 241 000 distinct taxa covered in it [about `r round(236023/240708, digits=4)*100`% of taxa in the NCBI taxonomy; @sanderson2008phylota] which in turn represent only about 10% of all extant described biodiversity [taking a conservative estimate of extant diversity; @scott2011ncbi; @federhen2003taxonomy].
In comparison, the current GenBank release number 238 (June 15, 2020) has tripled in size, hosting data for more than 217 million DNA sequences [(See GenBank's release website)](https://ftp.ncbi.nih.gov/genbank/gbrel.txt). Yet, the phylogeneyic potential of the database has not been attained yet, with data on phylogenetic relationships available for about 90 000 taxa [@hinchliff2015synthesis; CURRENT SYNTH TREE CITATION], representing only one third of the taxonomic diversity with data available a decade ago (or 3% of the whole diversity) ALSO COMPARE WITH NUMBER OF TAXA REPRESENTED IN GENEBANK TODAY. Some of this discrepancy is explained by the many phylogenies that are not publicly shared [@drew2013lost; @magee2014dawn, @mctavish2018bioessay]. However, most recently published large trees have been made available in recent years, indicating there is also a lag between the amount of new DNA data generated and the analysis of these data in a phylogenetic context.
